---
title: "Lab2"
author: "Kathryn Denning"
date: "1/20/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup and data import, echo = FALSE, warning = FALSE, message=FALSE, error=FALSE}
library(rio)
library(here)
library(tidyverse)
library(magrittr)
library(psych)
knitr::opts_chunk$set()

df <- import('https://github.com/fivethirtyeight/data/raw/master/alcohol-consumption/drinks.csv')
head(df)
str(df)
```

Density plot
compare the default bandwidth with a few other selections entered manually.
settle on a bandwidth selection, and justify why briefly in text
```{r histogram}
describe(df$total_litres_of_pure_alcohol)

ggplot(df, aes(x = total_litres_of_pure_alcohol)) +
  geom_histogram(bins = 100)
```

The datacamp suggested that as long as your n of observations is greater than 150 you should use bins = 100 (and this data has an n = 193). After exploring what smaller bins looked like, I decided that using bins = 100 seemed to display the data more realistically, meaning that it showed the variation in number of litres to a smaller amount in the distribution. I had thought of making bins = 15 because that corresponded better to the range, but the lack of gaps between bars overlooked the more nuanced differences between the number of litres people drank. Thus, I decided to go with bins = 100.

